A Switching Planner for Combined Task and Observation Planning

### 2011-04-21 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/switching.tex
Hi Moritz, I have merged the material I think we should have added to the paper...

We now describe our {\em switching} planning system that operates
according to the continual planning paradigm, given a description of
the current problem and domain in DTPDDL. The system {\em
switches}, in the sense that planning proceeds in interleaved
sessions, in which the base planner is either {\em sequential}/linear
or {\em decision-theoretic}.
%%
During a sequential session, a rewarding {\em trace} of a possible
execution is computed using a cost-optimising satisficing planner
which trades action costs, goal rewards, and determinacy.
%%
Formatted as a linear plan, the trace specifies a sequence of actions
that achieves some reachable goals following a deterministic
approximation of the problem at hand.
%%
Structurally, a trace is a sequence of elements that are either: (i) ground
actions from the DTPDDL description of the world, or (ii) atomic {\em
assumptions}, modelled as deterministic actions, made about the truth
value of facts that can only be determined at runtime (e.g., that a
box of cornflakes is located on the corner bench in the kitchen).
%%
The system always begins in a sequential session, so that plan
execution proceeds by applying DTPDDL actions from the trace, in
sequence, until the outcome of executing the next scheduled action is
too uncertain according to a threshold parameter~(here, 95\%). In that
eventuality a DT session commences, which tailors sensory processing
to determine whether the assumptions made in the trace hold, or which
otherwise acts to achieve the goals.

Because online DT planning in large problems is impractical (we seek
response times in seconds), a DT session plans for an abstract process
determined by the current trace and underlying belief-state. That
abstract problem is characterised by a limited number of propositions,
chosen due to their {\em relevance} to the action whose scheduled
execution triggered the switch to the DT session.
%%the subproblem the DT session is asked tosolve.
% MOG: Describe this in detail in the appropriate subsection
%  This
% abstraction is constructed by first excluding all propositions (and
% related actions) that are not true, or {\em assumed } true, of states
% in the trace, then adding them back, using as an heuristic the entropy
% of the trace assumptions conditional on a candidate
% proposition. Propositions are added, one at a time, until the number
% of states in the initial belief-state reaches a given
% threshold.\footnote{Our experiments are performed using a number of
% different threshold parameters.} 
To that abstract model we also add {\em disconfirm} and {\em confirm}
actions that the DT session can schedule in order to judge an atomic
assumption in the trace. Those actions yield a relatively small reward
if the corresponding judgement is true (or small penalty
otherwise). If a judgement action is scheduled for execution the DT
session is terminated, and control is returned to a new sequential
session.

Whatever the session type, our continual planner maintains a factored
representation of successive belief-states by performing belief
revision. As an internal representation of the $(\pp{:init})$
declaration, we keep a tree-shaped Bayesian network which gets updated
whenever an action is performed, or an observation received. That
belief-state representation is used: (1) as the source of candidate
determinisations for sequential planning, (2) in determining when to
switch to a DT session, and (3) as a mechanism to guide construction
of an abstract process for DT sessions.

@@

\small
\begin{tabular}{cccc}
\hline
Probability & (is-in R2D2)  & (is-in box)  & (is-in cup) \\
\hline
%% .24 & kitchen & office & office \\
%% .06 & kitchen & kitchen & office \\
%% .56 & kitchen & office & kitchen \\
%% .14 & kitchen & kitchen & kitchen \\
.7 & kitchen & \# &  kitchen\\
.3 & kitchen & \# & office \\
.8 & kitchen & office & \# \\
.2 & kitchen & kitchen & \# \\
1.0 & kitchen & \# & \# \\
\hline
\end{tabular}
\normalsize

\noindent Each assumption corresponds to one distinct {\em
relaxed} visitation of the root term. Here, a conjunctive term is
visited iff its atomic subterms are visited, and zero or one of its
immediate probabilistic subterms are visited. For a sequential
session, the starting state corresponds to an assumption (usually
unique) with probability $1$.\footnote{To simplify the discussion, we
suppose that the root term of $(\pp{:init})$ lists all atoms that are
necessarily true.} In our example, that starting state is:

@@

Encapsulating state-assumptions, we annotate the problem posed during
a sequential session with an \emph{assumptive action} $\assumptiveS{i}$ for
each element $\prob_i (T_i)$, of each probabilistic term from
$(\pp{:init})$. Here, $\assumptiveS{i}$ can be executed if no
$\assumptiveS{j}$, $j \neq i$, has been executed from the same
probabilistic term, and, either
$(\pp{probabilistic}~..\prob_i~(T_i)..)$ is in the root conjunct, or
it occurs in $T_k$ for some executed $\assumptiveS{k}$.
%%
We also add constraints that forbid scheduling of
assumptions about facts after actions with preconditions or effects
that mention those facts. For example, the robot cannot assume it is
plugged into a power source immediately after it unplugs itself.
%%
Executing $\assumptiveS{i}$ in a state $\state$ effects a transition
to a successor state $\state^{T_i}$ with probability $\prob_i$, and
$\state^\bot$ with probability $1 - \prob_i$. Here, $\state^{T_i}$ is
the union of $\state$ with atomic terms from $T_i$. State
$\state^\bot$ is an added sink.

We now describe the optimisation criteria used during sequential
sessions. Where $\prob_i$ is the probability that the $i^{th}$
sequenced action, $\action_i$, from a trace of state-action pairs
$\langle \state_0, \action_0,\state_1, \action_1,.., \state_N \rangle$
does not transition to $\state^\bot$, we have that the optimal trace
has value:

@@

\noindent  Here,  $\reward(\state_i, \action_i)$ is the instantaneous
reward ---i.e., can be negative for action costs, or positive for goal
achievement--- received for executing action $\action_i$ in state
$\state_i$. Finally, it is worth clarifying that in practise we do not
artificially limit the length of traces that the sequential planner
can consider. Moreover, for problems we consider there is always a
finite optimal trace.

@@

\noindent where $\$(T_i)$ (resp. $\hat\$(T_i)$) is a
small positive (negative) numeric quantity which captures
the utility the agent receives for correctly (incorrectly) rejecting
an assumption.
%%
In terms of action physics, a disconfirm action can only be executed
once, and otherwise is modelled as self-transformation.
%%
We only consider {\em relevant} assumptions when constructing the
abstract model.  If \switchAction\ is the action that switched the
system to a DT session, then an assumption $\assumptiveS{i}$ is {\em
relevant} if it is necessary for the outcome of \switchAction\ to be
determined.  Continuing our simplified example, if the trace is:

\small
\[
\begin{array}{l}
\actions^{\circ}(.8;(=(\pp{is-in}~\pp{box})\pp{office}));\\
\actions^{\circ}(.3;(=(\pp{is-in}~\pp{cup})\pp{kitchen}));\\
(\pp{look}~\pp{box}~\pp{office});
(\pp{look}~\pp{cup}~\pp{kitchen});\\
(\pp{report}~\pp{box}~\pp{office}); 
(\pp{report}~\pp{cup}~\pp{kitchen})
\end{array}
\]
\normalsize

@@

\Omit{
%%
Finally, 
If an
assumption was rejected, we prohibit that sequential session from
making it again.
}

%%  the size of the state space
%% is determined by two factors: the number of non-zero states in the
%% initial belief-state, and the number of actions. Determining
%% action reachability is intractable, as is determining their relevance
%% to goal achievement.

%% As we are aiming to keep the decision theoretic session fast, we try
%% to keep the state space of the abstract problem as small as
%% possible. In a deterministic-action POMDP, the state space size is
%% determined by two factors: the number of non-zero states in the
%% initial belief-state and the number of executable actions. As
%% determining the relevance of an action for a given goal in in general
%% a hard problem, we concentrate on keeping the number of uncertain
%% facts as low as possible without losing important information about
%% the sensing goal.

In order to guarantee fast DT sessions, planning occurs for a small
abstract problem. In our setting, where the underlying decision
process has a deterministic action model, a significant cause of
problem largeness is due to the number of states that occur with
non-zero probability in the underlying belief-state. In posing a small
abstract process for a DT session, we construct an abstract
belief-state that is chiefly characterised by facts related to the
current trace. In that abstraction, instances of operator or sense
declarations whose specification mentions an excluded fact are not
available.
%%
In detail, we first construct an $(\pp{:init})$ declaration which
contains the root term, and relevant assumptions from the trace --
e.g., (Fig.\ref{fig:abstraction-b}) gives an example fragment, where
diamonds are probabilistic terms, and circles are atomic and/or
conjunctive.
%%
For each excluded atom, we compute the {\em entropy} of the active
assumptions, {\em conditional} on that atom. Intuitively, lower
entropy indicates an atom gives better information about
assumptions. Facts are iteratively added to the belief-state in
increasing order according to that measure until the belief space size
reaches a predefined limit (Fig.\ref{fig:abstraction-c}).

%%  or no more atoms that reduce the entropy
%% can be added

\begin{figure}[h!]
  \centering
  \tikzstyle{tree} = [sibling distance=4.5mm]
  \tikzstyle{toplevel} = [grow'=right, sibling distance=22mm]
  \tikzstyle{seclevel} = [sibling distance=9mm]
  \tikzstyle{pnode} = [diamond, draw=black, minimum size=2.5mm]
  \tikzstyle{cnode} = [circle, draw=black, minimum size=3mm]
  \tikzstyle{assumption} = [solid, very thick, draw=black]
  \tikzstyle{selected} = [solid, draw=black]
  \tikzstyle{unused} = [densely dashed, draw=black!40]
  %% \subfloat[The initial belief-state with the assumptions made by the continual
  %%   planner in bold.]{
  %%     \label{fig:abstraction-a}
  %%     \begin{tikzpicture}[
  %%   level 3/.style={tree}]
  %%   \node[pnode, assumption] (cat) at (1,1) {} [toplevel]
  %%     child[seclevel] {node[cnode, assumption] (office) {}
  %%       child {node [pnode, assumption] (box) {}
  %%         child {node [cnode] (boxp1) {}}
  %%         child {node [cnode, assumption] (boxp2) {}}
  %%       }
  %%       child {node [pnode] (cup) {} 
  %%         child {node [cnode] (cupp1) {}}
  %%         child {node [cnode] (cupp2) {}}
  %%       }
  %%     }
  %%     child {node[cnode] (kitchen) {}
  %%       child {node [pnode] (box2) {} 
  %%         child {node [cnode] (box2p1) {}}
  %%         child {node [cnode] (box2p2) {}}
  %%       }
  %%     };
  %%  \tiny
  %%  \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
  %%  \node[above=0 of cat] {$\pp{(category room1)}$};
  %%  \node[below=0 of kitchen] {$\pp{kitchen}$};
  %%  \node[below=0 of office] {$\pp{office}$};
  %%  \node[below=0 of box] {$\pp{(is-in box)}$};
  %%  \node[below=0 of box2] {$\pp{(is-in box)}$};
  %%  \node[below=0 of cup] {$\pp{(is-in cup)}$};
  %%  \node[right=0 of boxp1] {$\pp{place1}$};
  %%  \node[right=0 of boxp2] {$\pp{place2}$};
  %%  \node[right=0 of box2p1] {$\pp{place1}$};
  %%  \node[right=0 of box2p2] {$\pp{place2}$};
  %%  \node[right=0 of cupp1] {$\pp{place1}$};
  %%  \node[right=0 of cupp2] {$\pp{place2}$};
  %%   % \node[node] (kitchen) right of (cat) {};
  %% \end{tikzpicture}}
\qquad
  \subfloat[Removing facts that are not part of an assumption.]{
    \label{fig:abstraction-b}
    \begin{tikzpicture}[
    level 3/.style={tree}]
    \node[pnode, assumption] (cat) at (1,1) {} [toplevel, unused]
      child[seclevel] {node[cnode, assumption] (office) {}
        child {node [pnode, assumption] (box) {}
          child {node [cnode, unused] (boxp1) {}}
          child {node [cnode, assumption] (boxp2) {}}
        }
        child {node [pnode, unused] (cup) {} 
          child {node [cnode, unused] (cupp1) {}}
          child {node [cnode, unused] (cupp2) {}}
        }
      }
      child {node[cnode, selected] (kitchen) {}
        child {node [pnode, selected] (box2) {} 
          child {node [cnode, unused] (box2p1) {}}
          child {node [cnode, selected] (box2p2) {}}
        }
      };
   \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
   \draw[selected] (cat) -- (kitchen) -- (box2) -- (box2p2);
   \tiny
   \node[above=0 of cat] {$\pp{(category room1)}$};
   \node[below=0 of office] {$\pp{office}$};
   \node[below=0 of box] {$\pp{(is-in box)}$};
   \node[below=0 of box2] {$\pp{(is-in box)}$};
   \node[right=0 of boxp2] {$\pp{place2}$};
   \node[right=0 of box2p2] {$\pp{place2}$};
    % \node[node] (kitchen) right of (cat) {};
  \end{tikzpicture}}
\vspace{2mm}
  \subfloat[Refinement, by adding relevant facts.]{
    \label{fig:abstraction-c}
    \begin{tikzpicture}[
    level 3/.style={tree}]
    \node[pnode, assumption] (cat) at (1,1) {} [toplevel, unused]
      child[seclevel] {node[cnode, assumption] (office) {}
        child {node [pnode, assumption] (box) {}
          child {node [cnode, selected] (boxp1) {}}
          child {node [cnode, assumption] (boxp2) {}}
        }
        child {node [pnode, unused] (cup) {} 
          child {node [cnode, unused] (cupp1) {}}
          child {node [cnode, unused] (cupp2) {}}
        }
      }
      child {node[cnode, selected] (kitchen) {}
        child {node [pnode, selected] (box2) {} 
          child {node [cnode, selected] (box2p1) {}}
          child {node [cnode, selected] (box2p2) {}}
        }
      };
   \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
   \draw[selected] (box) -- (boxp1);
   \draw[selected] (cat) -- (kitchen) -- (box2) -- (box2p2);
   \draw[selected] (box2) -- (box2p1);
   \tiny
   \node[above=0 of cat] {$\pp{(category room1)}$};
   \node[below=0 of office] {$\pp{office}$};
   \node[below=0 of box] {$\pp{(is-in box)}$};
   \node[below=0 of box2] {$\pp{(is-in box)}$};
   \node[right=0 of boxp1] {$\pp{place1}$};
   \node[right=0 of boxp2] {$\pp{place2}$};
   \node[right=0 of box2p1] {$\pp{place1}$};
   \node[right=0 of box2p2] {$\pp{place2}$};
    % \node[node] (kitchen) right of (cat) {};
  \end{tikzpicture}}

  \caption{Abstract belief-state, and refinement.}
\label{fig:abstraction}
\end{figure}

% When limiting the number of actions, we aim to include those that are
% possibly required to a) reach the goal or b) to directly observe an
% atom that is part of the abstract belief state. In general, checking
% this for an action is \textsc{PSPACE} complete for \textsc{STRIPS}
% planning.

% We approximate the set of relevant actions as follows: Let
% \relevantAtoms\ be the set of atoms that either occur in the goal
% condition \poss(\switchAction) or in a precondition \poss($a$) of an
% action $a$ that can directly sense any atom in the abstract belief
% state. We construct a \emph{relaxed planning graph} with
% \relevantAtoms\ as goal atoms from which we extract a relaxed
% plan.

%% In the first step, we remove all facts that are not part of an
%% assumption (Fig. \ref{fig:abstraction-b}). At this point, the session
%% would proceed in an abstraction of the environment that does not
%% contain $\pp{place1}$, the $\pp{cup}$ or a $\pp{kitchen}$. 
%% %%
%% In a second step, we iteratively refine the relaxed declaration by
%% adding terms from the original statement of $(\pp{:init})$ while the
%% number of abstract states in $\bstate_0$ that occur with non-zero
%% probability according to that refined declaration remains of a
%% practicable size. In detail,

>>>>

\newcommand{\entropy}{\ensuremath{\mathrm{H}}}

We now describe our {\em switching} planning system that operates
according to the continual planning paradigm. The system {\em
switches} in the sense that planning and plan execution proceed in
interleaved sessions in which the {\em base planner} is either {\em
sequential} or {\em decision-theoretic}.  The first session is
sequential, and begins when a DTPDDL description of the current
problem and domain are posted to the system.  During a sequential
session a serial plan is computed that corresponds to one
execution-{\em trace} in the underlying decision-process. That trace
is a reward-giving sequence of process actions and {\em assumptive}
actions. Each {\em assumptive} action corresponds to an assertion
about the truth of a fact that is unknown at plan time -- e.g. that a
box of cornflakes is located on the corner bench in the kitchen. The
trace specifies a plan and characterises a {\em deterministic
approximation} (see~\cite{yoon:etal:2008}) of the underlying process
in which that plan is valuable. Traces are computed by a
cost-optimising classical planner which trades off action costs, goal
rewards, and determinacy. Execution of a trace proceeds according to
the process actions in the order that they appear in the trace. If,
according to the underlying belief-state, the outcome of the next
action scheduled for execution is not predetermined above a threshold
(here 95\%), then the system switches to a DT session.

Because online DT planning is impractical for the size of problem we
are interested in, DT sessions plan in a small abstract problem
defined in terms of the trace from the proceeding sequential
session. This abstract state-space is characterised by a limited
number of propositions, chosen due to their {\em relevance} to the
action whose scheduled execution triggered the switch to the DT
session.  To allow the DT planner to judge assumptions from the trace,
we add {\em disconfirm} and {\em confirm} actions to the problem for
each of them. Those yield a relatively small reward/penalty if the
corresponding judgement is true/false. If a judgement action is
scheduled for execution, then the DT session is terminated, and a new
sequential session begins.

Whatever the session type, our continual planner maintains a factored
representation of successive belief-states.  As an internal
representation of the $(\pp{:init})$ declaration, we keep a
tree-shaped Bayesian network which gets updated whenever an action is
performed, or an observation received. That belief-state
representation is used: (1) as the source of candidate
determinisations for sequential planning, (2) in determining when to
switch to a DT session, and (3) as a mechanism to guide construction
of an abstract process for DT sessions.

@@

\small
\begin{tabular}{cccc}
\hline
Probability & (is-in R2D2)  & (is-in box)  & (is-in cup) \\
\hline
.7 & kitchen & \# &  kitchen\\
.3 & kitchen & \# & office \\
.8 & kitchen & office & \# \\
.2 & kitchen & kitchen & \# \\
1.0 & kitchen & \# & \# \\
\hline
\end{tabular}
\normalsize

\noindent Each assumption corresponds to one distinct {\em
relaxed} visitation of the root term. Here, a conjunctive term is
visited iff its atomic subterms are visited, and zero or one of its
immediate probabilistic subterms are visited. For a sequential
session, the starting state corresponds to an assumption (usually
unique) with probability $1$.\footnote{Without a loss of generality,
we assume conjunctive terms list atoms that are true with
probability 1 according to a visitation, and that actions do not
have negative preconditions.}  In our example, that starting state is:

@@

To represent state assumptions we augment the problem posed during
a sequential session with an \emph{assumptive action} $\assumptiveS{i}$ for
each element $\prob_i (T_i)$, of each probabilistic term from
$(\pp{:init})$. Here, $\assumptiveS{i}$ can be executed if no
$\assumptiveS{j}$, $j \neq i$, has been executed from the same
probabilistic term, and, either
$(\pp{probabilistic}~..\prob_i~(T_i)..)$ is in the root conjunct, or
it occurs in $T_k$ for some executed $\assumptiveS{k}$.
%%
We also add constraints that forbid scheduling of
assumptions about facts after actions with preconditions or effects
that mention those facts. For example, the robot cannot assume it is
plugged into a power source immediately after it unplugs itself.
%%
Executing $\assumptiveS{i}$ in a state $\state$ effects a transition
to a successor state $\state^{T_i}$ with probability $\prob_i$, and
$\state^\bot$ with probability $1 - \prob_i$. Here, $\state^{T_i}$ is
the union of $\state$ with atomic terms from $T_i$. State
$\state^\bot$ is an added sink.

We now describe the optimisation criteria used during sequential
sessions. Let $\prob_i$ be the probability that the $i^{th}$ sequenced
action, $\action_i$, from a trace of state-action pairs
$\langle \state_0, \action_0,\state_1, \action_1,.., \state_N \rangle$
does not transition to $\state^\bot$, and
$\reward(\state_i, \action_i)$ be the instantaneous reward received
for executing action $\action_i$ in state $\state_i$. The optimal
trace has value:

@@

@@

\noindent where $\$(T_i)$ (resp. $\hat\$(T_i)$) is a
small positive (negative) numeric quantity which captures
the utility the agent receives for correctly (incorrectly) rejecting
an assumption.
%%
In terms of action physics, a disconfirm action can only be executed
once, and otherwise is modelled as a self-transformation.
%%
We only consider {\em relevant} assumptions when constructing the
abstract model.  If \switchAction\ is the action that switched the
system to a DT session, then an assumption $\assumptiveS{i}$ is {\em
relevant} if it is necessary for the outcome of \switchAction\ to be
determined.  Continuing our simplified example, if the trace is:

\small
\[
\begin{array}{l}
\actions^{\circ}(.8;(=(\pp{is-in}~\pp{box})\pp{kitchen}));\\
\actions^{\circ}(.3;(=(\pp{is-in}~\pp{cup})\pp{office}));\\
(\pp{look}~\pp{box}~\pp{kitchen});
(\pp{look}~\pp{cup}~\pp{office});\\
(\pp{report}~\pp{box}~\pp{kitchen}); 
(\pp{report}~\pp{cup}~\pp{office})
\end{array}
\]
\normalsize

@@

%%%%

In order to guarantee fast DT sessions, those plan in an abstract
process determined by the current trace and underlying belief-state.
%%
The abstract process posed to the DT planner is constructed by first
constraining as statically false all propositions except those which
are true with probability 1, or which are the subject of {\em
relevant} assumptions. For example, taking the above trace and
switching action {\texttt (look~box~office)}, the underlying
belief in Fig.~\ref{fig:beliefs}B would determine a fully
constrained belief given by Fig.~\ref{fig:beliefs}C.
%%
Next, static constraints are removed, one proposition at a time, until
the number of states that can be true with non-zero probability in the
initial belief of the abstract process reaches a given threshold.
%%
In detail, for each statically-false proposition we compute the {\em
entropy} of the state assumptions of the current trace {\em
conditional} on that proposition. 
%%
Let $X$ be a set of propositions and $2^X$ the powerset of $X$, then taking

\small
\[
\chi = \{\bigwedge_{x \in X'
  \cap X}x \; \land \bigwedge_{x \in X \setminus X'}\neg x \;|\; X' \in 2^X\},
\]
\normalsize

\noindent we have that $\chi$ is a set of conjunctions each of which
corresponds to one truth assignment to elements in $X$. Where
$p(\phi)$ gives the probability that a conjunction $\phi$ holds in the
belief-state of the DTPDDL process, the entropy of $X$
\emph{conditional} on a proposition $y$, written $\entropy(X|y)$, is
given by Eq.~\ref{eq:condent}.

\vspace{-1ex}
\small
\begin{equation}\label{eq:condent}
  \entropy(X|y) = \sum_{x \in \chi, y' \in \{y, \neg y\}} p(x \land y') \log_2
  \frac{p(y')}{p(x \land y')}
\end{equation}
\normalsize

A low $\entropy(X|y)$ value suggests that knowing the truth value of
$y$ is useful for determining whether or not some assumptions $X$
hold. When removing a static constraint on propositions during the
abstract process construction, $y_i$ is considered before $y_j$ if
$\entropy(X|y_i)~<~\entropy(X|y_j)$. For example, if the serial plan
assumes the robot is in a kitchen, then propositions about the
contents of kitchens, e.g. {\texttt (=(is-in~cup)kitchen)}, are
added to characterise the abstract process' states. Taking
assumption $X$ to be {\texttt (=(is-in~box)kitchen)}, in relaxing
static constraints the following entropies are calculated:

\small
\begin{tabtt}
.47 \= = \entropy(\=X|(=(is-in~milk)office))\+ \\
 = \entropy(X|(=(is-in~milk)kitchen)) \-\\
.97 = \entropy(X|(=(is-in~cup)office))\+\\
 = \entropy(X|(=(is-in~cup)kitchen))
\end{tabtt}
\normalsize

\noindent Therefore, the first static constraint to be relaxed is for
\texttt{(=(is-in~milk)office)}, or
equivalently \texttt{(=(is-in~milk)kitchen)}, giving a refined
abstract belief state depicted in
Fig.~\ref{fig:beliefs}A. Summarising, if for Fig.\ref{fig:beliefs}B
the DT session is restricted to belief-states with fewer than $8$
elements, then the starting belief-state of the DT session does not
mention a ``cup''.

\begin{figure}
\tiny
\begin{tabularx}{\columnwidth}{XX}
\hline
\vspace{1ex}
\scriptsize (A) Partially constrained abstract \mbox{\hspace{4ex}belief-state} & 
\vspace{1ex}\scriptsize \hspace{-4ex}(B) Underlying DTPDDL belief \\
\vspace{-2ex} 
\begin{tabtt}
(\=:init (=(is-in~R2D2)kitchen) \+ \\
       (\=.6(and\=(=(is-in~box)kitchen) \+\+ \\
        (\=.9(=(is-in~milk)~kitchen))\+\\
         .1(=(is-in~milk)office))\-\-  \\
       .4(and(=(is-in~box)office) \+\\
        (.1(=(is-in~milk)kitchen))\+\\
        .9(=(is-in~milk)office)))
\end{tabtt} &
\vspace{-2ex} 
\begin{tabtt}
\hspace{-6ex}(\=:init (=(is-in~R2D2)office) \+ \\
       (\=.6(and\=(=(is-in~box)kitchen) \+\+ \\
        (\=.9(=(is-in~milk)kitchen))\+\\
         .1(=(is-in~milk)office))\-\-  \\
       .4(and(=(is-in~box)office) \+\\
        (.1(=(is-in~milk)kitchen))\+\\
        .9(=(is-in~milk)office))) \-\-\-\\
       (\=.6(=(is-in~cup)office) \+ \\
      .4(=(is-in~cup)kitchen))) \\
\end{tabtt} \\
\vspace{-6ex}\scriptsize(C) Fully constrained abstract \mbox{\hspace{5ex}belief-state} & \\
\vspace{-5ex} \begin{tabtt}
(\=:init (=(is-in~R2D2)kitchen) \+ \\
       (\=.6(=(is-in~box)kitchen))) \\
\end{tabtt} & \\
\hline
\end{tabularx}
\caption{Simplified examples of abstract belief-states from
       DT sessions. \label{fig:beliefs}}
\normalsize
\end{figure}
